Cross-Loop Optimization of Arithmetic Intensity for Finite Element Local Assembly

### 2014-10-20 TACO-paper-v2/coffee.tex
edited files

This research is partly funded by the MAPDES project, by the
Department of Computing at Imperial College London, by EPSRC through
grants EP/I00677X/1, EP/I006761/1, and EP/L000407/1, by NERC grants
NE/K008951/1 and NE/K006789/1, by the U.S.  National Science
Foundation through grants 0811457 and 0926687, by the U.S. Army
through contract W911NF-10-1-000, and by a HiPEAC collaboration
grant. The authors would like to thank Dr. Carlo Bertolli,
Dr. Lawrence Mitchell, and Dr. Francis Russell for their invaluable
suggestions and their contribution to the Firedrake project.

@@

Experiments were run on a single core of two Intel architectures, a
Sandy Bridge (I7-2600 CPU, running at 3.4GHz, 32KB L1 cache and 256KB
L2 cache) and a Xeon Phi (5110P, running at 1.05Ghz in native mode,
32KB L1 cache and 512KB L2 cache). We have chosen these two
architectures because of the differences in the number of logical
registers and SIMD lanes (16 256-bit registers in the Sandy Bridge,
and 32 512-bit registers in the Xeon Phi), which can impact the
optimization strategy. The \texttt{icc 13.1} compiler was used. For what concerns the compilation flags, we selected the best optimization levels on each platform: \texttt{-O2}, and \texttt{-xAVX} for auto-vectorization, were used on the Sandy Bridge; \texttt{-O3} was adopted on the Xeon Phi.

>>>>

This research is partly funded by the MAPDES project, by the
Department of Computing at Imperial College London, by EPSRC through
grants EP/I00677X/1, EP/I006761/1, and EP/L000407/1, by NERC grants
NE/K008951/1 and NE/K006789/1, by the U.S.  National Science
Foundation through grants 0811457 and 0926687, by the U.S. Army
through contract W911NF-10-1-000, and by a HiPEAC collaboration
grant. The authors would like to thank Dr. Carlo Bertolli,
Dr. Lawrence Mitchell, and Dr. Francis Russell for their invaluable
suggestions and their contribution to the Firedrake project.
We thank the ACM TACO reviewers for their suggestions that led
to a significantly improved version.

@@

Experiments were run on a single core of two Intel architectures, a
Sandy Bridge (I7-2600 CPU, running at 3.4GHz, 32KB L1 cache and 256KB
L2 cache) and a Xeon Phi (5110P, running at 1.05Ghz in native mode,
32KB L1 cache and 512KB L2 cache). We have chosen these two
architectures because of the differences in the number of logical
registers and SIMD lanes (16 256-bit registers in the Sandy Bridge,
and 32 512-bit registers in the Xeon Phi), which can impact the
optimization strategy. The \texttt{icc 13.1} compiler was used.  We
selected the best optimization levels for each platform using the
following compilation flags: \texttt{-xAVX} for auto-vectorization and
\texttt{-O2} were used on the Sandy Bridge; \texttt{-O3} was adopted
on the Xeon Phi.
